% Major Project Report
\documentclass[12pt,a4paper]{report}

% Required packages
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{booktabs}

% Document settings
\geometry{a4paper, margin=1in}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

% Title page information
\title{Major Project Report}
\author{Your Name}
\date{\today}

\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
This document presents the comprehensive report of the major project undertaken as part of the academic curriculum. The report details the project objectives, methodology, implementation, results, and conclusions.
\end{abstract}

% Table of Contents
\tableofcontents

% Chapter 1: Introduction
\chapter{Introduction}
\section{Project Overview}
This section provides an overview of the project, its objectives, and significance.

\section{Problem Statement}
Describe the problem that your project aims to solve.

\section{Project Goals}
List the specific goals and objectives of your project.

% Chapter 2: Literature Review
\chapter{Literature Review}
\section{Background}
Provide background information and context for your project.

\section{Related Work}
Discuss previous work and research related to your project.

% Chapter 3: Methodology
\chapter{Methodology}
\section{Project Approach}
Describe the overall approach and methodology used in your project.

\section{Technical Stack}
List and explain the technologies, tools, and frameworks used.

\section{Implementation Details}
Provide detailed information about the implementation process.

% Chapter 4: Results and Discussion
\chapter{Results and Discussion}
\section{Project Outcomes}
Present the results and outcomes of your project.

\section{Analysis}
Analyze the results and discuss their implications.

% Chapter 5: Conclusion
\chapter{Conclusion}
\section{Summary}
Summarize the key findings and achievements of the project.

\section{Future Work}
Discuss potential future improvements and extensions.

% References
\chapter{References}
% Add your references here

% Appendices
\appendix
\chapter{Appendix A}
% Add appendix content here

\end{document} 